It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
some edits

\subsection*{Known unknowns}
Systems often make decisions without having complete knowledge of all the
factors that affect, or could be affected by, these decisions.  For example, a
caching system evicts items based on what it thinks future requests will look
like, even though it cannot actually know what the future will look like. Here,
decisions are made in anticipation of future events.  In other cases, this
incomplete knowledge is due to the absence of data-computation locality. For
example, a load balancer makes decisions based on what it thinks is the current
load on other machines rather than what it actually is.

In both of these situations, assumptions are made about the unknowns offline in
\emph{design-time}--resulting in different routing and caching
algorithms. A change to the \emph{run-time} environment could render these
decisions wildly inefficient. By deferring to an ML agent, these decisions can
be made online, and can be nimble in adapting to any changes to the run-time
environment.

>>>>

\subsection*{Known unknowns}

Systems often make decisions without complete knowledge of the factors that affect,
or could affect, those decisions.  For example, a caching system evicts items based
on what it believes future requests will look like, without actually knowing the future.
In other cases, incomplete knowledge is due to the absence of data-computation locality.
For example, a load balancer makes decisions based on what it thinks the current load on
machines is, e.g. based on data it collected recently, rather than the actual load at that
very instant in time.

In both of these situations, assumptions are made about the unknowns offline during
\emph{design time}, resulting in different routing and caching algorithms. A change to
the \emph{run-time} environment could easily render these choices suboptimal.

\ignore{Online learning has the potential to make these decisions online, based on current contexts,
and can be nimble in adapting to any changes to the run-time
environment.}
